О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-18 pps-linear-bound/pps-linear-lower-bound.tex
Add a ref about dense circular rational set

However, Problems~\ref{prb:square_side_length_and_diameter_power} and~\ref{prb:square_side_length_and_diameter_linear}
do not seem to show the way for improving the estimate
due to the following well-known theorem (TODO: refs!).
\begin{theorem}
	\label{thm:rational_set_on_circle}
	There exists a dense subset $P$ of the unit circle such that for any $P_1, P_2 \in P$
	the distance $|P_1 P_2|$ is rational.
\end{theorem}
We conjecture that thorough investigation of existing examples of circular integral point sets
(TODO: refs!)
will lead to the negative answers for the
Problems~\ref{prb:square_side_length_and_diameter_power} and~\ref{prb:square_side_length_and_diameter_linear}.

>>>>

However, Problems~\ref{prb:square_side_length_and_diameter_power} and~\ref{prb:square_side_length_and_diameter_linear}
do not seem to show the way for improving the estimate
due to the following well-known theorem,
which can be proved by an application of inversion~\cite{solymosi2010question}.
\begin{theorem}
	\label{thm:rational_set_on_circle}
	There exists a dense subset $P$ of the unit circle such that for any $P_1, P_2 \in P$
	the distance $|P_1 P_2|$ is rational.
\end{theorem}
We conjecture that thorough investigation of existing examples of circular integral point sets
(TODO: refs!)
will lead to the negative answers for the
Problems~\ref{prb:square_side_length_and_diameter_power} and~\ref{prb:square_side_length_and_diameter_linear}.
